---
title: "Does sunshine make people happy?"
author: "F. Rodriguez-Sanchez"
date: "20 January 2020"
output: html_document
---


## Introduction

It is well known that individual well-being can be influenced by climatic conditions. However, ...


## Methods

```{r echo=FALSE} 
## Read data
data <- read.table("data.txt", header = TRUE)
# correct error
data <- data[-12, ]

# Fit linear model
model <- lm(happiness ~ sunshine, data = data)

```

We collected data on `r nrow(data)` individuals and fitted a linear model:

$$
y = \alpha + \beta x + \epsilon 
$$



## Results

We found that happiness is positively related to sunshine hours (slope = `r round(coef(model)[2], digits = 2)`).

```{r echo=FALSE}
# Print results
library(xtable, quietly = TRUE)
knitr::kable(xtable(model)) 
```

```{r echo=FALSE}
# Plot
visreg::visreg(model)
```

## Discussion

These results confirm that sunshine is good for happiness.


## Acknowledgements

Y. Xie, J. MacFarlane, Rstudio...


```{r echo=FALSE, eval=FALSE}
sessionInfo()
```

## Cited references
